Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

There are some possible solutions to assign the value.

@@

\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss the alias symbol that points to the same memory cell.

We propose to combine both the information from the source code and the runtime to align the memory access during the execution. At the point the memory is allocated, we use the tuple $(start\ address, length)$ to represent the buffer. In the following execution, we check if any memory access falls into the range of these tuples. If so, we add the memory access into the tuple. After the execution, the tuple can be mapped into the location of the source code, and we only compare the memory access that belongs to the same lines in the source code.

>>>>

There are two types of possible solutions to assign the value.

@@

\textbf{Source Code Information.} Alternatively, we can use the information from the source code. Recent work~\cite{sumner2010memory} proposes using the execution point that allocates the memory cell as the index and tracking the pointer arithmetic to track the pointer that points to the memory. However, such a method may miss aliased symbols that point to the same memory cell.

We propose to combine both the information from the source code and the runtime to align the memory access during the execution. At the point the memory is allocated, we use the tuple $\texttt{(start\ address, length)}$ to represent the buffer. In the following execution, we check if any memory access falls into the range of these tuples. If so, we add the memory access into the tuple. After the execution, the tuple can be mapped into the location of the source code, and we only compare the memory access that belongs to the same lines in the source code.
